Precise Weed and Maize classification through Convolutional Neuronal Networks

### 2017-07-13 PaperBCJ.tex
Fixes of Green Channel
Fix redaction and picture of green Channel

Then, through a digital image processing, the images were segmented to differentiate them from the soil and other non-plant elements, then the images were masked to provide the dataset features of color of the Maize and Weed. Once the segmented images were obtained, they were removed those that had a resolution lower than 64x64 pixels, because it's smaller than size of input layer of the network, besides it was not convenient its processing since its total area was much smaller than the samples of corn, which is the purpose of this document, later, the images were saved in a png format. The process described before, was illustrated in the next figure. \\
	\begin{figure}[h]
	\centering
	\includegraphics[width=3.2in]{procesamiento}
	\caption{Preprocessing to obtain samples for the dataset}
	\label{fig_sim}
	\end{figure}

>>>>

Then, through a digital image processing, as first stage the image was normalized in its green channel, it improves the detection of green color due it eliminates lights and shadows of the image, after we extracted the green color to obtain a grayscale image, through the next equation described by Wang, Meng, Luo and Mei \cite{wang2013path}, then we applied a OTSU Thresholding to grayscale image in order to obtain a binary mask.  
\begin{equation}
	S = 2*G - R - B
\end{equation} 
After the images were segmented to differentiate them from the soil and other non-plant elements, the original images were masked to provide the dataset features of color of the Maize and Weed. Once the segmented images were obtained, they were removed those that had a resolution lower than 64x64 pixels, because it's smaller than size of input layer of the network, besides it was not convenient its processing since its total area was much smaller than the samples of corn, which is the purpose of this document, later, the images were saved in a png format. The process described before, was illustrated in the next figure. \\
	\begin{figure}[h]
	\centering
	\includegraphics[width=3.2in]{procesamiento}
	\caption{Preprocessing to obtain samples for the dataset}
	\label{fig_sim}
	\end{figure}
